---
title: "HW2"
output: pdf_document
date: "09/05/2024"
header-includes:
   - \usepackage{amsmath}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Q1(a) \begin{align*} 
R(T,a,b) &= MSE_{a,b}(T(X))\\
&= Var_{a,b}(T(X)) + (Bias_{a,b}(T(X)))^{2}\\
\end{align*} \begin{align*}
Var_{a,b}(T(X)) &= Var_{a,b}(\frac{1}{n}\sum_{i=1}^{n}X_{i})\\
&= \frac{1}{n^{2}}\sum_{i=1}^{n}Var_{a,b}(X_{i})\\
&= \frac{b^{2}\pi^{2}}{3n}\\
\end{align*} \begin{align*}
(Bias_{a,b}(T(X)))^{2} &= (\mathbb{E}_{a,b}(T(X))-a)^{2}\\
&= (\mathbb{E}_{a,b}(\frac{1}{n}\sum_{i=1}^{n}X_{i})-a)^{2}\\
&= (\frac{1}{n}\sum_{i=1}^{n}\mathbb{E}_{a,b}(X_{i})-a)^{2}\\
&= (\frac{1}{n}\sum_{i=1}^{n}a-a)^{2}\\
&= 0\\
\end{align*} \begin{align*}
R(T,a,b) &= Var_{a,b}(T(X)) + (Bias_{a,b}(T(X)))^{2}\\
&= \frac{b^{2}\pi^{2}}{3n}\\
\end{align*} (b) \begin{align*}
R(U,a,b) &= MSE_{a,b}(U(X,c))\\
&= Var_{a,b}(U(X,c)) + (Bias_{a,b}(U(X,c)))^{2}\\
\end{align*} \begin{align*}
Var_{a,b}(U(X,c)) &= Var_{a,b}(\frac{c}{2}+\frac{1}{2n}\sum_{i=1}^{n}X_{i})\\
&= \frac{1}{4n^{2}}\sum_{i=1}^{n}Var_{a,b}(X_{i})\\
&= \frac{b^{2}\pi^{2}}{12n}\\
\end{align*} \begin{align*}
(Bias_{a,b}(U(X,c)))^{2} &= (\mathbb{E}_{a,b}(U(X,c))-a)^{2}\\
&= (\mathbb{E}_{a,b}(\frac{c}{2}+\frac{1}{2n}\sum_{i=1}^{n}X_{i})-a)^{2}\\
&= (\frac{c}{2}+\frac{1}{2n}\sum_{i=1}^{n}\mathbb{E}_{a,b}(X_{i})-a)^{2}\\
&= (\frac{c}{2}+\frac{1}{2n}\sum_{i=1}^{n}a-a)^{2}\\
&= (\frac{c}{2}+\frac{a}{2}-a)^{2}\\
&= \frac{(c-a)^{2}}{4}\\
\end{align*} \begin{align*}
R(U,a,b) &= Var_{a,b}(U(X,c)) + (Bias_{a,b}(U(X,c)))^{2}\\
&= \frac{b^{2}\pi^{2}}{12n}+\frac{(c-a)^{2}}{4}\\
\end{align*} (c) Given $a\in[-5,5],b=3,c=1$ and $n=10$.

```{r risk, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3, fig.width=5, fig.align="center"}
# Initialize parameters
a = seq(-5, 5, by = 0.001) # Produce 10000 values for the parameter of interest
b = 3
c = 1
n = 10

# Create function to calculate Risk as a function of the parameters values and estimator
T = b^2*pi^2/(3*n)

# Evaluate this function for different parameter values and estimators
U = T/4+(c-a)^2/4

# Load necessary packages to plot risk functions
library(ggplot2)
library(dplyr)
library(scales)
library(grid)
library(gridExtra)
library(ggthemes)

# Group risk function in a data frame
df = data.frame("a" = a, "T" = T, "U"=U)
colors <- c("T (X)" = "red", "U (X,c)" = "blue")

# Plot result with labels
ggplot() + 
  geom_line(data = df, aes(x = a, y = T, color = "T (X)"), size = 1.2, linetype = "dashed") +
  geom_line(data = df, aes(x = a, y = U, color = "U (X,c)"), size = 1.2, linetype = "dashed") +
  xlab("a") +
  ylab("Risk")+
  xlim(c(-5.0, 5.0))+
  ylim(c(0.000, 10.000))+
  labs(title = "Risk function comparison", color = "Estimators")+
  scale_color_manual(values = colors)+theme_economist_white()+scale_fill_economist()+
  theme(plot.title = element_text(size=12, hjust = 0))+
  theme(axis.text=element_text(size=8), axis.title=element_text(size=10,face="bold"), legend.text = element_text(size = 8), legend.title = element_text(size = 8))


```

(d) Observed that T(X) is constant with respect to a, the minimax estimator is $T(X) = \operatorname*{argmin}_{\{T,U\}}\max_{a} R$.
